AP/PA Tables ITHIM Global

### 2023-08-26 injury_tables.Rmd
added output version control

---
title: "Injury Outcomes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
---

@@

```{r load_objects = "asis"}
# Assumes that multi_city_script.R has been run - read in ithim_objects saved as io.rds
io <- readRDS("results/multi_city/io.rds")

# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']

@@

@@

@@

# write to csv
readr::write_csv(inj_counts_list, paste0('results/multi_city/inj/inj_counts.csv')) # table containing all the fatality counts
```

@@

# output csv
readr::write_csv(rd, 'results/multi_city/inj/injury_risks_per_billion_kms.csv')
```

@@

# write to csv
readr::write_csv(injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'), 'results/multi_city/inj/injury_risks_per_100k_pop.csv')
```

@@

# write to csv
readr::write_csv(true_distances_df, 'results/multi_city/inj/distances.csv')
```

@@

# write as csv
readr::write_csv(rd_hours, 'results/multi_city/inj/injury_risks_per_100million_h.csv')
```

```{r}
# Export injury datasets as a single excel file
path_inj_wb <- "results/multi_city/inj/inj_data.xlsx"
 writexl::write_xlsx(list(inj_counts = inj_counts_list, #%>% filter(str_mode != 'Total'),
                          injury_risks_billion_kms = rd,
                          injury_risks_100k_people  = injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'),
                          injury_risks_100mil_h = rd_hours,
                          true_distances = true_distances_df),
                     path = path_inj_wb)
```

>>>>

---
title: "Injury Outcomes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  output_version: ''
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
---

@@

```{r load_objects = "asis"}
output_version <- "v0.3"

# Assumes that multi_city_script.R has been run - read in ithim_objects saved as io.rds
io <- readRDS(paste0("results/multi_city/io_", output_version, ".rds"))

# Get names of cities from the io object
cities <- names(io)[!names(io) %in% c('scen_prop','ithim_run' )]

@@

# input parameter file name
input_parameter_file <<- io$ithim_run$input_parameter_file

# further model run information
compute_mode <- io$ithim_run$compute_mode 
timestamp_model <- io$ithim_run$timestamp
comments_model <- io$ithim_run$comment

@@

# print model run information to screen:
cat("  \n")
cat(paste0('Output version: ', output_version)) 
cat("  \n")
cat(paste0('Timestamp of model run: ', timestamp_model))
cat("  \n")
cat(paste0('Comments from model run: ', comments_model))
cat("  \n")

@@

# write to csv
readr::write_csv(inj_counts_list, paste0('results/multi_city/inj/inj_counts_',output_version,'.csv')) # table containing all the fatality counts
```

@@

# output csv
readr::write_csv(rd,paste0( 'results/multi_city/inj/injury_risks_per_billion_kms_',output_version,'.csv'))
```

@@

# write to csv
readr::write_csv(injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'), paste0('results/multi_city/inj/injury_risks_per_100k_pop_',output_version,'.csv'))
```

@@

# write to csv
readr::write_csv(true_distances_df, paste0('results/multi_city/inj/distances_',output_version,'.csv'))
```

@@

# write as csv
readr::write_csv(rd_hours, paste0('results/multi_city/inj/injury_risks_per_100million_h_',output_version,'.csv'))
```

```{r}
# Export injury datasets as a single excel file
path_inj_wb <- paste0('results/multi_city/inj/inj_data_',output_version,'.xlsx')
 writexl::write_xlsx(list(inj_counts = inj_counts_list, #%>% filter(str_mode != 'Total'),
                          injury_risks_billion_kms = rd,
                          injury_risks_100k_people  = injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'),
                          injury_risks_100mil_h = rd_hours,
                          true_distances = true_distances_df),
                     path = path_inj_wb)
```

### 2023-08-26 summary_tables.Rmd
added output version control

---
title: "Summary Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

@@

### - output .csv/.xlsx files containing the following information:

@@

```{r load_objects = "asis", echo = F, message = F}

# read in io object which is produced at the end of an ITHIM-Global run
# Assumes that multi_city_script.R has been run 
io <- readRDS("results/multi_city/io.rds")

# Get names of cities from the io object
cities <<- names(io)[!names(io) %in% 'scen_prop']

@@

# find reference scenario
ref_scen <- io[[cities[1]]]$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen) # update scen name

@@

## Distance categories

@@

# calculate ylls by age category and scenario
# i.e. sum over all disease and remove sex 
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:NSCEN,function(y){# loop through scenarios
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)]) # sum over all diseases
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z])) # sum age categories ignoring sex
  })
  colnames(temp) <- hb_scen_names_upd # update scenario names
  temp
})

@@

# extract population statistics
pop_by_age <- lapply(io[-2], function(x)
  sapply(unique(x$demographic$age), 
         function(y)
           sum(subset(x$demographic, age == y)$population)
         )
  )

@@

# calculate the total ylls for each scenario summing across all diseases
yll_totals <- lapply(io[-2], function(x) {
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,c('sex','age_cat')], 1,
                          function(z)paste0(z[2], '_', z[1]))
  colnames(temp) <- orig_scen_names_updated
  temp
})

@@

# calculate change in YLLs due to injury by summing across all age categories for the injury results
injury_totals <- lapply(io[-2], function(x) {
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  injury_col <- grep("inj", names(xx))[1] 
  xxx <- sapply(1:NSCEN, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- hb_scen_names_upd
  xxx
})

@@

# sum the YLLs for each scenario by age category
pa_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN, function(y){
    xxx <- rowSums(xx[, pa_yll_cols[seq(y, length(pa_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- hb_scen_names_upd
  xxx
})

@@

# sum the YLLs by scenario and age category
ap_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    xxx <- rowSums(xx[, ap_yll_cols[seq(y, length(ap_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- hb_scen_names_upd
  xxx
})

@@

# sum the total deaths by scenario
disease_totals <- lapply(io[-2],function(x){
  # extract disease counts
  xx <- x$outcomes$hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub"))) 
  xxx <- sapply(1:NSCEN,function(y){ # sum over scenarios
    colSums(xx[, seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- hb_scen_names_upd

@@

# sum the total ylls by scenario
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- hb_scen_names_upd

@@

for (k in measure) { # loop for ylls or deaths
  for (j in pathway) { # loop for hb or pathway_hb
    for (i in names(io[-2])) { # loop for cities

@@

# Export ylls HB
write.csv(ylls,
            "results/multi_city/health_impacts/ylls.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            "results/multi_city/health_impacts/ylls_pathway.csv",
            row.names = F)
# Export deaths HB
write.csv(deaths,
            "results/multi_city/health_impacts/deaths.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            "results/multi_city/health_impacts/deaths_pathway.csv",
            row.names = F)

>>>>

---
title: "Summary Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  output_version: ''
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

@@

### - output .csv files containing the following information:

@@

```{r load_objects = "asis", echo = F, message = F}
#output_version <- "v0.3"
# read in io object which is produced at the end of an ITHIM-Global run
# Assumes that multi_city_script.R has been run 
# read in input file
io <- readRDS(paste0("results/multi_city/io_", output_version, ".rds"))

# Get names of cities from the io object
cities <- names(io)[!names(io) %in% c('scen_prop','ithim_run' )]

@@

# input parameter file name
input_parameter_file <<- io$ithim_run$input_parameter_file

# scenario and reference scenario definitions
scenario_name <- io$ithim_run$scenarios_used
ref_scen <- io$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen)

# further model run information
compute_mode <- io$ithim_run$compute_mode 
timestamp_model <- io$ithim_run$timestamp
comments_model <- io$ithim_run$comment

@@

# Distance categories

@@

# calculate ylls by age category and scenario
# i.e. sum over all disease and remove sex 
yll_totals <- lapply(io[-c(2,3)],function(x){
  temp <- sapply(1:NSCEN,function(y){# loop through scenarios
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)]) # sum over all diseases
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z])) # sum age categories ignoring sex
  })
  colnames(temp) <- hb_scen_names_upd # update scenario names
  temp
})

@@

# extract population statistics
pop_by_age <- lapply(io[-c(2,3)], function(x)
  sapply(unique(x$demographic$age), 
         function(y)
           sum(subset(x$demographic, age == y)$population)
         )
  )

@@

# calculate the total ylls for each scenario summing across all diseases
yll_totals <- lapply(io[-c(2,3)], function(x) {
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,c('sex','age_cat')], 1,
                          function(z)paste0(z[2], '_', z[1]))
  colnames(temp) <- orig_scen_names_updated
  temp
})

@@

# calculate change in YLLs due to injury by summing across all age categories for the injury results
injury_totals <- lapply(io[-c(2,3)], function(x) {
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  injury_col <- grep("inj", names(xx))[1] 
  xxx <- sapply(1:NSCEN, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- hb_scen_names_upd
  xxx
})

@@

# sum the YLLs for each scenario by age category
pa_totals <- lapply(io[-c(2,3)],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN, function(y){
    xxx <- rowSums(xx[, pa_yll_cols[seq(y, length(pa_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- hb_scen_names_upd
  xxx
})

@@

# sum the YLLs by scenario and age category
ap_totals <- lapply(io[-c(2,3)],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    xxx <- rowSums(xx[, ap_yll_cols[seq(y, length(ap_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- hb_scen_names_upd
  xxx
})

@@

# sum the total deaths by scenario
disease_totals <- lapply(io[-c(2,3)],function(x){
  # extract disease counts
  xx <- x$outcomes$hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub"))) 
  xxx <- sapply(1:NSCEN,function(y){ # sum over scenarios
    colSums(xx[, seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- hb_scen_names_upd

@@

# sum the total ylls by scenario
disease_totals <- lapply(io[-c(2,3)],function(x){
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- hb_scen_names_upd

@@

for (k in measure) { # loop for ylls or deaths
  for (j in pathway) { # loop for hb or pathway_hb
    for (i in names(io[-c(2,3)])) { # loop for cities

@@

# Export ylls HB
write.csv(ylls,
            paste0('results/multi_city/health_impacts/ylls_',output_version,'.csv'),
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            paste0('results/multi_city/health_impacts/ylls_pathway_',output_version,'.csv'),
            row.names = F)
# Export deaths HB
write.csv(deaths,
            paste0('results/multi_city/health_impacts/deaths_',output_version,'.csv'),
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            paste0('results/multi_city/health_impacts/deaths_pathway_',output_version,'.csv'),
            row.names = F)

### 2023-08-26 summary_tables_PA_AP.Rmd
added output version control

---
title: "AP/PA Tables ITHIM Global"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    toc: true
    toc_depth: 5
    toc_float: true
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

###### Read in input parameters

# Assumes that multi_city_script.R has been run  
# read in input file
io <- readRDS("results/multi_city/io.rds")

# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']

@@

# initialise parameters using first city in list
city <- cities[1]
scen_length <- length(io[[city]]$ithim_run$scenario_names) - 1

# input parameter file name
input_parameter_file <<- io[[city]]$ithim_run$input_parameter_file

# scenario and reference scenario definitions
scenario_name <- io[[city]]$ithim_run$scenarios_used
ref_scen <- io[[cities[1]]]$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen)

compute_mode <- io[[city]]$ithim_run$compute_mode

@@

# create output Excel file containing the basic PM2.5 and CO2 exposure / concentration information
output_file <- "results/multi_city/AP/desc_stats.xlsx"
writexl::write_xlsx(list(PM_2.5_emission_inventory = sl,
                         CO2_conc = co2_conc,
                         summary_stats_PM2.5_CO2 = bind_rows(l)), path = output_file)

# create csv file (summary_stats_Pm2.5_CO2 tab in Excel file above)
write_csv(bind_rows(l), "results/multi_city/AP/desc_stats.csv")

>>>>

---
title: "AP/PA Tables ITHIM Global"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  output_version: ''
output:
  html_document: 
    toc: true
    toc_depth: 5
    toc_float: true
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

###### Read in input parameters
output_version <- output_version

# Assumes that multi_city_script.R has been run  
# read in input file
io <- readRDS(paste0("results/multi_city/io_", output_version, ".rds"))

# Get names of cities from the io object
cities <- names(io)[!names(io) %in% c('scen_prop','ithim_run' )]

@@

# initialise parameters using first city in list
city <- cities[1]
scen_length <- length(io$ithim_run$scenario_names) - 1

# input parameter file name
input_parameter_file <<- io$ithim_run$input_parameter_file

# scenario and reference scenario definitions
scenario_name <- io$ithim_run$scenarios_used
ref_scen <- io$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen)

# further model run information
compute_mode <- io$ithim_run$compute_mode 
timestamp_model <- io$ithim_run$timestamp
comments_model <- io$ithim_run$comment

@@

# create output Excel file containing the basic PM2.5 and CO2 exposure / concentration information
output_file <- paste0('results/multi_city/AP/desc_stats_', output_version ,".xlsx")
writexl::write_xlsx(list(PM_2.5_emission_inventory = sl,
                         CO2_conc = co2_conc,
                         summary_stats_PM2.5_CO2 = bind_rows(l)), path = output_file)

# create csv file (summary_stats_Pm2.5_CO2 tab in Excel file above)
write_csv(bind_rows(l), paste0('results/multi_city/AP/desc_stats_', output_version ,".csv"))
